EDA

### 2020-03-01 src/EDA&mode_fitting.Rmd
typo corrected.

ridge_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 0.55, family = 'gaussian', lambda = 0.009140377)
predictions_test <- predict(ridge_reg, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.566096

>>>>

elastic_reg = glmnet(x_train, y_train, nlambda = 25, alpha = 0.55, family = 'gaussian', lambda = 0.009140377)
predictions_test <- predict(elastic_reg, newx = x_test)
eval_results(y_test, predictions_test)
```
MSPE = 2.566096
